\documentclass[12pt]{extarticle}
\pagenumbering{gobble}
\usepackage{times}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[colorlinks=true,allcolors=MidnightBlue]{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{titlesec}
	\titleformat*{\section}{\scshape}
	\titleformat*{\subsection}{\normalfont}
\usepackage{enumitem}
	\setlist{nosep,leftmargin=*}
\usepackage{parskip}
\newcommand{\NAME}[1]{
	\begin{center}
		\large{#1}
	\end{center}
}
\newcommand{\SECTION}[1]{
	\section*{
		\raisebox{-2pt}{#1}
		\quad\leaders\hrule\hfill
	}
}
\newcommand{\LR}[2]{
	\subsection*{
		\makebox[\textwidth]{\textbf{#1}\hfill#2}%
	}
}
\newcommand{\LRLR}[4]{
	\subsection*{
		\makebox[\textwidth]{\textbf{#1}\hfill#2}
		\makebox[\textwidth]{#3\hfill#4}%
	}
}
\title{}
\author{}
\date{}
\begin{document}

\NAME{Gregory Lim Eu Rhen}

\vspace{4pt}
\begin{minipage}[t]{0.45\textwidth}
	E-mail: \href{mailto:gregorylimeurhen@gmail.com}{gregorylimeurhen@gmail.com}

	Website: \href{https://gregorylimeurhen.github.io}{gregorylimeurhen.github.io}
\end{minipage}
\hfill
\begin{minipage}[t]{0.55\textwidth}
	\raggedleft
	GitHub: \href{https://github.com/gregorylimeurhen}{github.com/gregorylimeurhen}

	LinkedIn: \href{https://linkedin.com/in/gregorylimeurhen}{linkedin.com/in/gregorylimeurhen}
\end{minipage}

% Accomplished [X] as measured by [Y], by doing [Z].
% [verb]'d a [noun] (that [blank] (to [blank])) to [blank]
\SECTION{Experiences}
\LRLR
{Creatz3D and Figure Factories}
{May 2025 to Sep 2025}
{AI Intern}
{Singapore}
\begin{itemize}
	\item Trained and tested graph neural networks on proprietary data to efficiently thicken meshes. % figure factories
	\item Set up AI orchestrations using n8n to continually generate image-enriched Shopify blog posts using Google, LinkedIn, Roblox, X (Twitter), and YouTube data. % figure factories
	\item Set up a UI for interacting with (large) language models on private local networks.
	% \item Built a tool to allow users to naturally prompt language models to complete web-based tasks using local web browsers.
	% \item Built a tool to allow users to privately edit videos. % figure factories
	% \item Built a tool that allows users to efficiently import Roblox Studio models in bulk from Roblox identifiers. % figure factories
\end{itemize}
\LRLR
{Singapore University of Technology and Design}
{Jan 2025 to Apr 2025}
{Teaching Assistant}
{Singapore}
\begin{itemize}
	\item Volunteered to help teach first-year undergraduate multivariable calculus and linear algebra.
\end{itemize}

\SECTION{Projects}
\begin{itemize}
	\item Introduced \textit{replay regularized attention}, a family of dreaming-inspired learning algorithms that aims to regularise feature representations by sampling and blending feature maps from a memory buffer during training.
	\begin{itemize}
		\item Trained and tested models on the Stanford Earthquake Dataset to accurately detect earthquake signals with and without the attention.
		\item Trained and tested models on a curated waste dataset to accurately detect object recyclability with and without the attention.
	\end{itemize}
	\item Introduced \textit{vibe decoding}, a 1-hyperparameter generalization of greedy decoding for autoregressive language models that aims to impart efficient semantic foresight by preferring next tokens which align with the expected semantic direction of the model in embedding space.
	\begin{itemize}
		\item Characterised the asymptotic runtime of the method.
		\item Characterised the hyperparameter interval for which the decoding becomes greedy.
		\item Tested instruction-tuned Qwen 2.5 0.5B, Gemma 2 2B, and Llama 3.1 8B on BoolQ, NumerSense, PG-19, and WikiText tasks using Macro F1, MRR, and PPL across various hyperparameter values.
		\item Studied a possible failure mode of the method relating to embedding space isotropy.
	\end{itemize}
\end{itemize}

\SECTION{Education}
\LRLR
{Singapore University of Technology and Design}
{Sep 2022 to Apr 2026}
{Bachelor's, Computer Science}
{Singapore}
\begin{itemize}
	\item \textbf{Cocurriculars.} Galois Group Mathematics Club, 3DC Google Developer Student Club.
\end{itemize}
\LRLR
{University of British Columbia}
{Jul 2023 to Aug 2023}
{Exchange, Linguistics and English History}
{Canada}
\begin{itemize}
	\item \textbf{Course average.} 92.5/100. % 92.5 = (88+97)/2
\end{itemize}

\SECTION{Skills}
\begin{itemize}
	\item \textbf{Deep learning frameworks.} Pytorch, TensorFlow.
	\item \textbf{Natural languages.} English, Chinese, Esperanto, Malay.
	\item \textbf{Source code languages.} C, CSS, HTML, Javascript, Jupyter Notebook, Lua, Makefile, Python, Shell, TeX, VBA.
\end{itemize}

\SECTION{Publications}
\begin{itemize}
	\item Lim, Gregory.
	(2025).
	\textit{Galois Parsimony.}
	Preprint.
	\href{https://philarchive.org/rec/LIMGPD}{http://philarchive.org/rec/LIMGPD}
\end{itemize}

\SECTION{Recognition}
\begin{itemize}
	\item \textit{50.040 Theory and Practice of Deep Learning Top Projects}, Singapore University of Technology and Design, 2025.
	\item \textit{Singtel Information Systems and Programming First Prize}, Singtel, 2024.
	\item \textit{10.015 Physical World 1D Project Award}, Singapore University of Technology and Design, 2022.
	% \item \textit{Top 6 Players by Fame}, Realm of the Mad God, 2022.
	\item \textit{Malay (Special Programme) Top in Cohort}, Temasek Secondary School, 2018.
	\item \textit{Math and Science Book Prize}, Temasek Secondary School, 2017.
\end{itemize}

% https://web.archive.org/web/20231029123705/https:/smt.sutd.edu.sg/education-and-design-awards/physical-world-design-1d-award/

\end{document}
